Variational Monte Carlo on bosonic systems

### 2018-03-25 project_1/article/article.tex
Quick maths!

\section{Derivation of Local Energy alpha derivative}

TO BE INSERTED HERE??? Or whaaaat boiii...

>>>>

\section{Variational parameter gradient of the expectation energy}
    Here we show how to arrive at the expression shown in
    \autoref{eq:variational_parameter_gradient}. This requires us to restrict
    our view to real trial wavefunctions, i.e., $\Psi_T^{*} = \Psi_T$, which is
    the case for the wavefunctions we are exploring.
    \begin{align}
        \nabla_{\alpha}\expval{E_L}
        &=
        \nabla_{\alpha}
        \para{
            \frac{
                \int\dd\vf{r}\Psi_T^{*}H\Psi_T
            }{
                \int\dd\vf{r}|\Psi_T|^2
            }
        }
        \\
        &=
        -
        \frac{
            2
            \para{
                \int\dd\vf{r}\Psi_T H\Psi_T
            }
        }{\para{\int\dd\vf{r}\Psi_T}^2}
        \int\dd\vf{r}\Psi_T\nabla_{\alpha}\Psi_T
        \\
        &\qquad
        +
        \frac{2}{\int\dd\vf{r}\Psi_T^2}
        \int\dd\vf{r}\Psi_TH\brak{
            \nabla_{\alpha}\Psi_T
        }
        \\
        &=
        - 2\expval{E_L}
        \frac{1}{
            \int\dd\vf{r}\Psi_T^2
        }
        \int\dd\vf{r}\Psi_T^2\para{
            \frac{\nabla_{\alpha}\Psi_T}{\Psi_T}
        }
        \\
        &\qquad
        +
        \frac{2}{\int\dd\vf{r}\Psi_T^2}
        \int\dd\vf{r}\Psi_T^2 E_L\para{
            \frac{\nabla_{\alpha}\Psi_T}{\Psi_T}
        }.
    \end{align}
    We now use the definition of the expectation value to group terms together.
    We are thus left with
    \begin{align}
        \nabla_{\alpha}\expval{E_L}
        =
        2
        \para{
            \expval{
                E_L\frac{1}{\Psi_T}\nabla_{\alpha}\Psi_T
            }
            - \expval{E_L}
            \expval{\frac{1}{\Psi_T}\nabla_{\alpha}\Psi_T}
        },
    \end{align}
    which is what we wanted to show.
